---
title: "SAS KNN project"
author: "Ryan Schubert"
date: "November 2, 2019"
output: html_document
---

```{r}
install.packages("tau")
install.packages("tm")
install.packages("cluster")
install.packages("hclust")
install.packages("SnowballC")
```


```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(data.table)
library(tm)
library(tau)
library(stats)
library(cluster)
library(SnowballC)
```

## R Markdown
To do:
Identify all unique tags deanonymize them if possible
create presence matrix per question id
create word tag frequency matrix
tag covariance/tag clustering via chisq test

```{r}
question_tags<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\tag_questions.csv",sep=",",header=T)
colnames(question_tags)
tags_dict<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\tags.csv",sep=",",header=T)
colnames(tags_dict)
question_tags<-inner_join(question_tags,tags_dict, by=c("tag_questions_tag_id"="tags_tag_id"))
question_tags$tag_questions_tag_id<-NULL
dim(question_tags)
length(unique(question_tags$tags_tag_name))
length(unique(question_tags$tag_questions_question_id))
tags<-as.data.frame(table(question_tags$tags_tag_name))
tags<- tags %>% filter(Freq >=100)

questions<-as.data.frame(table(question_tags$tag_questions_question_id))

question_tags<- question_tags %>% 
  filter(tags_tag_name %in% tags$Var1) %>%
  filter(tag_questions_question_id %in% questions$Var1)
tags$root<-substr(tags$Var1,1,4)
```
76553 unique question-tag pairs comprising
7091 semi-unique tags (tags may be misspelled, and not be truly unique)
23288 semi-unique questions 

After filtering 
51592 QT pairs
13580 questions
948 tags

after stric filtering
32755 QT pairs
13580 questions
143 tags

df is organized such that each row is a pair
I want a Q by T matrix, where each row is a question and each column is a tag
each entry is 0 if that tag is not present for the given question and 1 if the tag is present for the given question

```{r}
question_tags$tags_tag_name<-gsub("-","_",question_tags$tags_tag_name)
#QT_matrix<-table(question_tags$tag_questions_question_id,question_tags$tags_tag_name)
TQ_matrix<-table(question_tags$tags_tag_name,question_tags$tag_questions_question_id)


write.table(TQ_matrix,"C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\Tag_question_matrix_filtered.csv",sep=",",col.names = T,row.names = T)
```

```{r}
TQ_matrix<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\Tag_question_matrix_filtered.csv",header=T,sep=",")
TQ_matrix$root<-substr(TQ_matrix$tagID,1,4)
TQ_matrix$tagID<-NULL
test<-aggregate(. ~ root,data=TQ_matrix,sum)


write.table(test,"C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\Tag_question_matrix_by_aggregate.csv",sep=",",col.names = T,row.names = F)

test[test != 0] <- 1

write.table(test,"C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\Tag_question_matrix_by_aggregate_floor.csv",sep=",",col.names = T,row.names = F)

```

Create a term matrix for top 5 tags

```{r}

most_liked_tags<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\LikesToHighestTags.csv",header=T)
tags<-most_liked_tags %>% select(-maxLike,-sumLike,-nanswers) %>% mutate(sum = college + career + medicine + business + engineering) %>% filter(sum == 1)
preKNN<-tags %>% select(-sum)
preKNN<-melt(data = preKNN,varible=questionID) %>% filter(value == 1)

questions<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\questions.csv",header=T) %>% 
  filter(questions_id %in% preKNN$questionID) %>% 
  select(questions_id, questions_title)
questions_term<-tokenize(questions$questions_title) %>% 
  paste(collapse = " ") %>% 
  remove_stopwords(stopwords(kind="en"),lines=T)  %>% termFreq(control=list(removePunctuation=T))
test<-as.data.frame(questions_term)

nwords<-dim(test)[1]
nquestions<-dim(questions)[1]
question_term_matrix<-as.data.frame(matrix(0,nrow=nquestions,ncol = nwords))
rownames(question_term_matrix)<-questions$questions_id
colnames(question_term_matrix)<-rownames(test)
for (i in c(1:nquestions)){
  QI_tokens<-tokenize(questions$questions_title[i]) %>% 
    paste(collapse = " ") %>% 
    remove_stopwords(stopwords(kind="en"),lines=T)  %>% 
    termFreq(control=list(removePunctuation=T)) %>% 
    as.data.frame()
  QI_ID<-questions$questions_id[i]
  question_term_matrix[QI_ID,rownames(QI_tokens)]<-QI_tokens$.
}
colnames(preKNN)
preKNN<-select(preKNN,-value)
colnames<-c("questionID","class")
question_term_matrix$questionID<-rownames(question_term_matrix)
strict<-question_term_matrix[,colSums(question_term_matrix[,colnames(question_term_matrix) != "questionID"])>10]
strict$questionID<-rownames(strict)
strict$sum<-rowSums(strict[,colnames(strict) != "questionID"])
final<-inner_join(strict,preKNN,by="questionID")
fwrite(final,"C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\questions_term_freq_matrix_strict.csv",col.names = T,row.names = F)

initial<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\questions_term_freq_matrix.csv",header=T)
keep<-initial %>% select(-questionID,-class)
strict<-keep[,colSums(as.data.frame(keep))>10]
dim(keep)
test<-keep[,lapply(.SD,sum)]
str(strict)
```


Create term matrix for clustered data

```{r}
names<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\Quesion_tag_matrix_filtered_strict.csv",sep=",",header=T,select = "questionID") %>% unlist() %>% as.character()
complete_header<-c("questionID",names,"clusterID","distance")

clust30<-fread("C:\\Users\\rshoo\\Downloads\\Cluster_30.csv" , header=F,sep=",")
colnames(clust30)<-complete_header
dict30<-select(clust30,questionID,clusterID) %>% mutate(clust=paste("Clust",clusterID,sep=""))
QT_matrix<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\Quesion_tag_matrix_filtered_strict.csv",header = T, select="questionID")

questions<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\questions.csv",sep=",",header=T,drop="questions_date_added")
question_tags<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\tag_questions.csv",sep=",",header=T)
colnames(question_tags)
tags_dict<-fread("C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\tags.csv",sep=",",header=T)
colnames(tags_dict)
question_tags<-inner_join(question_tags,tags_dict, by=c("tag_questions_tag_id"="tags_tag_id"))
question_tags$tags_tag_name<-gsub("-","_",question_tags$tags_tag_name)
question_tags$tag_questions_tag_id<-NULL
colnames(question_tags)
colnames(dict30)
question_tags<-question_tags %>% inner_join(dict30,by=c("tags_tag_name"="questionID"))
colnames(questions)
colnames(question_tags)
question_tag_clusters<-select(question_tags,tag_questions_question_id,clust) %>% unique()
questions_single_cluster<-table(question_tag_clusters$tag_questions_question_id) %>% as.data.frame() %>% filter(Freq == 1 )
question_tag_clusters<-question_tag_clusters %>% filter(tag_questions_question_id %in% questions_single_cluster$Var1)
test<- questions %>% inner_join(question_tag_clusters,by=c("questions_id" ="tag_questions_question_id"))
questions<-questions %>% filter(questions_id %in% test$questions_id)

title_terms<-tokenize(questions$questions_title) %>% 
  paste(collapse = " ") %>% 
  remove_stopwords(stopwords(kind="en"),lines=T)  %>% termFreq(control=list(removePunctuation=T)) 
title_terms<-as.data.frame(title_terms)
title_terms$terms<-rownames(title_terms)
colnames(title_terms)<-c("Freq","terms")

body_terms<-tokenize(questions$questions_body) %>% 
  paste(collapse = " ") %>% 
  remove_stopwords(stopwords(kind="en"),lines=T)  %>% termFreq(control=list(removePunctuation=T))
body_terms<-as.data.frame(body_terms)
body_terms$terms<-rownames(body_terms)
colnames(body_terms)<-c("Freq","terms")
question_terms<-rbind.data.frame(body_terms,title_terms)


str(question_terms)
terms<-aggregate(x=question_terms$Freq,by=list(question_terms$terms),FUN=sum)
colnames(terms)<-c("term","freq")
final_terms<-filter(terms, freq >= 50)


nwords<-dim(final_terms)[1]
nquestions<-dim(questions)[1]
question_term_matrix<-as.data.frame(matrix(0,nrow=nquestions,ncol = nwords))
rownames(question_term_matrix)<-questions$questions_id
colnames(question_term_matrix)<-final_terms$term

for (i in c(1:nquestions)){
  
title_tokens<-tokenize(questions$questions_title[i]) %>% 
  paste(collapse = " ") %>% 
  remove_stopwords(stopwords(kind="en"),lines=T)  %>% termFreq(control=list(removePunctuation=T)) 
title_tokens<-as.data.frame(title_tokens)
title_tokens$tokens<-rownames(title_tokens)
colnames(title_tokens)<-c("Freq","tokens")

body_tokens<-tokenize(questions$questions_body[i]) %>% 
  paste(collapse = " ") %>% 
  remove_stopwords(stopwords(kind="en"),lines=T)  %>% termFreq(control=list(removePunctuation=T))
body_tokens<-as.data.frame(body_tokens)
body_tokens$tokens<-rownames(body_tokens)
colnames(body_tokens)<-c("Freq","tokens")
question_tokens<-rbind.data.frame(body_tokens,title_tokens)
tokens<-aggregate(x=question_tokens$Freq,by=list(question_tokens$tokens),FUN=sum)
colnames(tokens)<-c("tokens","freq")
tokens<-tokens %>% filter(tokens %in% final_terms$term)
indices<-as.character(unlist(tokens$tokens))

  QI_ID<-questions$questions_id[i]
  question_term_matrix[QI_ID,indices]<-tokens$freq
}
question_term_matrix$questionID<-rownames(question_term_matrix)
final<-inner_join(question_term_matrix,question_tag_clusters,by=c("questionID"="tag_questions_question_id"))
fwrite(final,"C:\\Users\\rshoo\\OneDrive\\Desktop\\Fall 2019\\stat 403 project\\Features_by_cluster_strict.csv",col.names = T,sep = ",",row.names = F,quote = F)
```

